\documentclass[10pt,letterpaper,sans]{moderncv}
\moderncvstyle{banking}%classic,banking,oldstyle,fancy,casual
\moderncvcolor{blue}

\usepackage{lastpage}
% \rfoot{\addressfont\itshape\textcolor{gray}{Page \thepage}}

\usepackage{url}
\usepackage{multicol}
% \usepackage{fontawesome}
% \usepackage[bottom]{footmisc} % enabling footnotes
% \usepackage{amsmath}
\usepackage[scale=0.94, footskip=0.5cm]{geometry} % Reduce document margins
\usepackage{mathptmx}
\setlength{\hintscolumnwidth}{0.5cm} % Uncomment to change the width of the dates column
\input{details}
\begin{document}
\clearpage
\makecvtitle{}
\vspace{-20pt}

% \section{Career Target}
% \colorlet{color1}{black}
% \subsection{\textbf{Software Engineer -- Computer Graphics}}
%  Put a couple sentences here
% New graduate looking to work with industry professionals utilizing the latest graphics APIs such as Vulkan and DirectX. 
% \vspace{10pt}
\definecolor{color1}{rgb}{0.22,0.45,0.70}%
\section{Key Qualifications}
\cvitem{$\bullet$}{Languages: C, \textbf{C++}, \textbf{C\#}, JavaScript, Ruby, SQL, XAML, HTML, CSS, and Java}
\cvitem{$\bullet$}{Software and Technologies: Visual Studio, Visual Studio Code, Unity, Unreal Engine, Game Maker Studio 2,  \textbf{OpenGL}}
\cvitem{$\bullet$}{.Net MAUI, Rest API, NodeJS, }
\cvitem{$\bullet$}{Experienced in developing in both Windows and Unix envirionments}
% \cvitem{$\bullet$}{Native English speaker with excellent verbal communication skills}
% \cvitem{$\bullet$}{Japanese language beginner able to read, write, and speak basic Japanese} 


\definecolor{color1}{rgb}{0.22,0.45,0.70}
\section{Education}
\colorlet{color1}{black}
\subsection{Bachelor of Science, Computer Science}
\cvitem{$\bullet$}{Western Washington University | \textbf{ABET Accredited} |  June 2024}
\subsection{Relevant Coursework:} 
\begin{multicols}{3}
\cvitem{$\bullet$}{Algorithms}
\cvitem{$\bullet$}{Operating Systems}
\cvitem{$\bullet$}{Networking}
\columnbreak
\cvitem{$\bullet$}{Game Programming}
\cvitem{$\bullet$}{Virtual Worlds}
\cvitem{$\bullet$}{Mobile Application Development}
\columnbreak
\cvitem{$\bullet$}{Object Oriented Design}
\cvitem{$\bullet$}{Secure Software Development}
\cvitem{$\bullet$}{Device Drivers - Developed drivers for both Windows and NetBSD}
\end{multicols}


\definecolor{color1}{rgb}{0.22,0.45,0.70}
\section{Employment}
\colorlet{color1}{black}

\subsection{Research Assistant Classroom Simulations (Sep23--Present)}
\cvitem{$\bullet$}{Coded a realistic classroom model in Unity using \textbf{C\#} that supports many actors that can independently initiate tasks in order to accomplish goals and cooperate with other agents.}
\cvitem{$\bullet$}{Programmed the animations of agents to creat a more realistic looking simulation.}

\subsection{Volunteer as a CS Tutor WWU (Jan23--Jun23)}
\cvitem{$\bullet$}{Tutored roughly ten students a week on fundamental Computer Science concepts such as object oriented programming, data structures, and computer systems in C, Python, Java, and Racket.}

% \subsection{Hawthorne Learning Solutions Tutor (Jan23--Feb23)}
% \cvitem{$\bullet$}{Tutored a student on fundamental computer systems concepts such as usage of the C language, bitwise operations, and x86 assembly language.}

\subsection{United States Navy Aviation Electronics Technician (June15--June19)}
\cvitem{$\bullet$}{Worked as a part of a team in a fast paced environment to reach mission critical deadlines every day.}
\cvitem{$\bullet$}{Troubleshot, diagnosed, and repaired avionics systems such as RADAR, SONAR, and radio communications.}
\cvitem{$\bullet$}{Handled, transported, and managed equipment requiring a secret clearance.}


% \vspace{10pt}
\definecolor{color1}{rgb}{0.22,0.45,0.70}%
\section{Projects}
\colorlet{color1}{black}

\subsection{\httplink[OpenGLRenderer]{github.com/dizzyj/OpenGLRenderer}}
\cvitem{$\bullet$}{Created a basic 3D renderer that can display multiple 3D objects that are dynamically lit by a light source using the Blinn-Phong model.}
\cvitem{$\bullet$}{Wrote various shaders that can apply an image texture to an object and simulate dynamic lighting  in the \textbf{OpenGl} Shading Language, GLSL.}
\cvitem{$\bullet$}{Coded the project in \textbf{C++} using CMake, GLAD, and GLFW.}

\subsection{\httplink[Mage Escape]{github.com/dizzyj/MageEscape}}
\cvitem{$\bullet$}{Worked in a team of four Game Developers to create a 3D person action puzzle game spanning two levels using \textbf{C\#} in the Unity game engine.}
\cvitem{$\bullet$}{Programmed animations for four different characters and many environmental objects such as chests, doors and torches.}
\cvitem{$\bullet$}{Designed and implemented  four enemy AI and combat behaviors.}
\cvitem{$\bullet$}{Designed and implemented the player UI}

\subsection{\httplink[Virtual World Builder System Plugin]{github.com/dizzyj/Virtual-World-BuilderSystem}}
\cvitem{$\bullet$}{Planned and implemented a system that allows users to build custom objects in a persistent virtual world with a team of three other developers.}
\cvitem{$\bullet$}{Identified, documented, and fixed major bugs.}


% \subsection{Additional Experience}
% \cvitem{$\bullet$}{Intern at Games For Love  (Apr23--Present)}
%\cvitem{$\bullet$}{One year of Japanese language education} I should either get more education or pass the JLPT test before putting this on here. 
%  \subsection{}
%  \cvitem{$\bullet$}{}   this is here for copy and pasting purposes lol
\end{document}